MS_Intro_Short

### 2022-05-17 Markdown/Manuscript/Child_RMDs/Doodles.Rmd
intro done

>>>>

10 rules [@Erdemir2020]
.....DARTH

[@Sampson2019] - 
development of networks of health economists that are working on a particular disease area. 
f reference models, open-source modelling, or model registries are to be part of the model development process, then standards need to be developed to guide analysts in achieving best practice. The availability of guidance can help to create confidence in researchers to pursue transparency. Yet, selecting the best standards to use can also be challenging [56]. Wider uptake—and appropriate use—of standards, by both modellers and journals, should be encouraged, and research should evaluate the suitability of guidance relating to transparency.
However, transparency depends on the code being well structured and clearly commented and a user or reviewer is required to have knowledge of the language in order to validate, use or adapt the model. There is a steep learning curve for analysts unfamiliar with script-based models
There may also be barriers in the communication of models due to a lack of knowledge for end users. However, this can be substantially mitigated with the use of open access interface packages, like the R package Shiny, which can be used to turn an R model into an interactive web application [58]. This allows a user without any R knowledge to use or, in part, validate the model.
Collaboration
----
@Erdemir2020] - 
We recommend the use of existing repositories for disseminating code and models.

there is a need for guidance, frameworks and templates
Guidance needed for implementation. Current transparency guidance not good enough.

ome resistence to adoption centers on.... [@Padula2017] . 
HE commercial...[@Feenstra2022],
   author]

A major shift in how health economic models are implemented.....They may also have educational value in developing the health systems modelling field [@Dunlop2017]. However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.

The health economics field i

cooperation [@Arnold2010]
coding framework / guidance [@Alarid2019]
10 rules [@Erdemir2020]
Sys review??

Maybe [@Feenstra2022] - 
Model complexity increases validation needs as does multi-purpose modelling
conceptual model, input data, computational model, operational model
International collaboration in validation
Need for documentation
Commercial ownership of HE models reduce scope for open-source
finances, accountability, and ownership barriers to OS
still not very widespread in HE decision model
would require more resources, could greatly increase transparency
distinguishing grades of open source
Model validation should hence become more structured and standardized, as well as more transparent.

Modular validation - Ghabri, Justifies extensive validation
Citing Dunlop - HE lagging behind other modelling fields

Australian
poor validation - ghabri

Over the last decade there have been
the potential to increase the transparency, reproducibility and reuse of health economic analyses.

Open source frameworks, which have been recommended for the development of mental health modelling field [@RN73], have the potential to help address a number of these challenges. Open source approaches can promote common standards and interoperability, improve model transparency and facilitate routine updates to rectify errors, update data and add features.

- Our project - readyforwhatsnext : open source model of the systems shaping the mental health of young people
- Lack of guidance on open source health economic models and in particular on recommended frameworks for implementing the computational model.
- Focus computational model. Most in need of novel guidance. Also: Of the three components that comprise a mental health computer simulation model - the conceptual model, the mathematical model and the computational model - only the first two are typically developed and reported in a manner that facilitates reuse, refinement and extension by others. This is problematic as the code implementation is where the theory represented by a simulation model is most fully elaborated.

### 2022-05-17 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
intro done

<!-- Add aims text here -->

>>>>

<!-- Add aims text here -->
As part of a project to develop an open source model of youth mental health, we have developed a framework that consolidates and refines these and other recommended standards for OSHEMs and provides a set of tools to help implement models that conform to these standards. In this paper we describe the rationale for and content of the framework we have developed and illustrate its practical application with a worked example.

### 2022-05-17 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
intro done

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Computational models have become an essential tool for healthcare policy development [@Erdemir2020]. Although influential and widely used, these models routinely contain errors [@Radeva2020], are often poorly reproducible [@Jalali2021; @McManus2019] and may be infrequently updated or revised [@Sampson2017]. To address these issues, there is increasing in principle support for open source health economics models (OSHEMs) that grant open access to and liberal permission to re-use model source code [@Pouwels2022]. However, in-practice implementation of OSHEMs remains rare [@Emerson2019]. Some resistence to adoption centers on.... [@Padula2017] .

A major shift in how health economic models are implemented.....They may also have educational value in developing the health systems modelling field [@Dunlop2017]. However, open source computational models also present a range of conceptual, technical, legal and resourcing issues compared to more traditional approaches to model development.

The health economics field i

copyrights, model misuse, confidential data, software, and time/resources [@Wu2019]
cooperation [@Arnold2010]
coding framework / guidance [@Alarid2019]
10 rules [@Erdemir2020]
Sys review
Over the last decade there have been
the potential to increase the transparency, reproducibility and reuse of health economic analyses.

Open source frameworks, which have been recommended for the development of mental health modelling field [@RN73], have the potential to help address a number of these challenges. Open source approaches can promote common standards and interoperability, improve model transparency and facilitate routine updates to rectify errors, update data and add features.

- Our project - readyforwhatsnext : open source model of the systems shaping the mental health of young people
- Lack of guidance on open source health economic models and in particular on recommended frameworks for implementing the computational model.
- Focus computational model. Most in need of novel guidance. Also: Of the three components that comprise a mental health computer simulation model - the conceptual model, the mathematical model and the computational model - only the first two are typically developed and reported in a manner that facilitates reuse, refinement and extension by others. This is problematic as the code implementation is where the theory represented by a simulation model is most fully elaborated.

>>>>

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Computational models have become an essential tool for healthcare policy development [@Erdemir2020]. Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017]. To help address these issues, there is increasing in principle support for open source health economics models (OSHEMs) that grant open access to and liberal permissions to re-use model source code [@Pouwels2022]. However, in-practice implementation of OSHEMs remains rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit adoption of OSHEMs [@Feenstra2022].

There is also a need to develop good practice guidance for implementing OSHEMs [@Sampson2019], which is currently scarce and piecemeal. Current health economist best practice guidelines on model transparency was published ten years ago [@Eddy2012] and contained recommendations on technical and non-technical model documentation but not about how model code and data are to be shared. More recent and more general guidance recommends the sharing of model code and data using repositories such as GitHub and Zenodo as well as the use of version control systems such as Git across the development lifecycle of a modelling project [@Erdemir2020]. A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions[@Alarid2019].
